\documentclass[10pt,letterpaper]{article}

% ----- Minimal, Overleaf-safe packages -----
\usepackage[
  ignoreheadfoot,
  top=1.6cm, bottom=1.6cm, left=1.6cm, right=1.6cm,
  footskip=0.6cm
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\definecolor{myblue}{RGB}{0,102,204}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{charter}
\usepackage{fontawesome5}

% ----- Basic setup -----
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\definecolor{primaryColor}{RGB}{0,0,0}
\hypersetup{colorlinks=true,urlcolor=primaryColor}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{5pt}{3pt}

% Bullets
\renewcommand{\labelitemi}{\textendash}
\newenvironment{highlights}{
  \begin{itemize}[topsep=2pt,parsep=1pt,partopsep=0pt,itemsep=0pt,leftmargin=10pt]
}{\end{itemize}}

% ----- Personal Info -----
\newcommand{\Name}{Md. Habib Ullah Yeasin}
\newcommand{\Role}{Flutter Developer}
\newcommand{\Location}{Zam Zam Tower, Mohakhali, Banani, Dhaka, Bangladesh}
\newcommand{\Email}{habibullahyeasin@outlook.com}
\newcommand{\Phone}{+880 1303 219937}
\newcommand{\LinkedIn}{https://linkedin.com/in/md-habib-ullah-yeasin}
% GitHub is not strictly required for PM but good to show tech background
\newcommand{\GitHub}{https://github.com/Yeasin84} 

\begin{document}

% ---------- Header ----------
\begin{center}
    {\fontsize{23pt}{23pt}\selectfont \Name}\par
    \vspace{2pt}
    {\Large \textcolor{myblue}{\Role}}\par
    \small
    \faMapMarker*~\Location \par
    \vspace{2pt}
    \faEnvelope~\href{mailto:\Email}{\Email} ~•~
    \faPhone~\href{tel:\Phone}{\Phone} ~•~
    \faLinkedin~\href{\LinkedIn}{LinkedIn} ~•~
    \faGithub~\href{\GitHub}{GitHub}
\end{center}

\vspace{3pt}

% ======================= SUMMARY =======================
\section{Professional Summary}
Results-driven Flutter Developer with \textbf{1+ years of practical experience} in building high-performance, cross-platform mobile applications. Proficient in \textbf{Dart}, \textbf{Flutter framework}, and \textbf{modern mobile architecture}. Expert in REST \textbf{API integration}, \textbf{JSON handling}, and complex state management using \textbf{Provider and Riverpod}. Passionate about collaborating with designers to implement pixel-perfect UI/UX and thriving in fast-paced production environments.
\vspace{5pt}

% ======================== SKILLS =========================
\section{Technical Skills}
\noindent
\textbf{Mobile Development:} Flutter, Dart, Android (Native Integration), iOS (Basic) \\[2pt]
\textbf{State Management:} Provider, Riverpod, GetX (Advanced), Async Programming (Futures/Streams) \\[2pt]
\textbf{Architecture:} Clean Architecture, MVC, MVVM, Dependency Injection \\[2pt]
\textbf{Backend \& API:} REST APIs, JSON Parsing, \textbf{Firebase (Auth, Firestore}, FCM, Storage) \\[2pt]
\textbf{Tools \& DevOps:} Git, GitHub, VS Code, Android Studio, \textbf{Postman (Certified)}, Figma

\vspace{5pt}

% ======================== PROJECTS =========================
\section{Flutter Development Experience}

% --- Project 1 ---
\textbf{AroggyaPath} $|$ \textit{Role: Lead Flutter Developer}
\hfill \href{https://github.com/Yeasin84/AroggyaPath.git}
{\textcolor{myblue}{\faGithub}}
\href{https://docs.google.com/presentation/d/10b3HphnqcUrSLe6pjGhUV1HGRvQXor6Jl4Ls2WsCkmc/edit?usp=sharing}{\textcolor{myblue}{\faFilePowerpoint}}\\
\textit{Comprehensive Healthcare Application}
\begin{highlights}
  \item \textbf{Architecture:} Built a scalable app using \textbf{Clean Architecture} principles to ensure maintainability and testability.
  \item \textbf{State Management:} Implemented Provider and Riverpod for efficient state \textbf{handling across complex user flows} (appointments, medical records).
  \item \textbf{API Integration:} \textbf{Integrated RESTful APIs} to fetch real-time health news and manage user data via JSON, ensuring smooth data synchronization.
  \item \textbf{Features:} Developed real-time appointment scheduling using \textbf{Firebase Firestore}, integrated FCM for \textbf{push notifications}, and implemented \textbf{secure Authentication}.
  \item \textbf{UI/UX:} Created a responsive, adaptive UI with dark/light mode switching, adhering to modern material design principles.
\end{highlights}

\vspace{5pt}

% --- Project 2 ---
\noindent
\textbf{GetX Showcase} \hfill \href{https://github.com/Yeasin84/getx_showcase}{\textcolor{myblue}{\faGithub}}\\
\textit{Advanced UI \& State Pattern Demo}
\begin{highlights}
  \item Demonstrated mastery of \textbf{reactive programming} and dependency injection.
  \item Implemented advanced \textbf{routing and theme management}, showcasing deep knowledge of the Flutter Framework.
\end{highlights}

\vspace{5pt}

% ======================= EDUCATION =======================
\section{Education}
\noindent\begin{tabularx}{\linewidth}{@{}X>{\raggedleft\arraybackslash}p{4.3cm}@{}}
\textbf{University of Frontier Technology, Bangladesh}\\[-3pt]
\textbf{B.Sc. in Educational Technology and Engineering (EdTEE)}
&
\shortstack[r]{Jan 2020 -- Jan 2025\\ CGPA: 3.28/4.00}
\end{tabularx}

\vspace{1pt}
\textit{A multidisciplinary program integrating software development, instructional design, networking, and engineering principles.}\\[3pt]
\textbf{Relevant Coursework:} Mobile Application Development, Data Structures \& Algorithms, OOP, Database Management Systems, Networking, Software Engineering, Database Systems, Cloud Computing, Testing \& QA.
\vspace{5pt}

% ======================== CERTIFICATIONS =========================
\section{Certifications}
\begin{highlights}
  \item \textbf{SQL (Basics) Certified (HackerRank)} -- Validates strong relational database knowledge.
  \href{https://www.hackerrank.com/certificates/539f8885f96a}{\textcolor{myblue}{\faExternalLink*}}
  \item \textbf{Postman API Fundamentals Student Expert – Postman, 2025}
  \href{https://badges.parchment.com/public/assertions/fN9nswpfR1WrnmD2XuL_bQ}{\textcolor{myblue}{\faExternalLink*}}
  
  \item \textbf{AWS Academy Graduate:} Introduction to Cloud (2025)
  \href{https://www.credly.com/badges/a7885fd8-c50d-4134-ba82-bb392fe1f139}{\textcolor{myblue}{\faExternalLink*}}
  
  \item \textbf{CS Fundamentals With Phitron (2025)} -- Focus on C++ and Data Structures.
  \href{https://phitron.io/course-details/batch3}{\textcolor{myblue}{\faExternalLink*}}
  
  \item \textbf{Soft Skill: 21st Century Core Employability Skills Development Program – Wadhwani Foundation, 2023} 
  \href{https://web.certificate.wfglobal.org/en/certificate?certificateId=657185118c30de8667bdadc4}{\textcolor{myblue}{\faExternalLink*}}\\
  Achieved 90\% score in the “Competencies of Job Ready Modules” under Wadhwani Opportunity’s global workforce readiness initiative.
\end{highlights}


\end{document}
